Housing Default Handovers

### 2024-04-23 minos/validation/housing_handovers.Rmd
tweaking scripts for running transitions/make

>>>>

## Heating

```{r}
raw.heating <- raw.dat %>%
  dplyr::select(pidp, time, heating) %>%
  group_by(time, heating) %>%
  count() %>%
  mutate(source = 'final_US')

base.heating <- base.dat %>%
  dplyr::select(pidp, time, heating) %>%
  group_by(time, heating) %>%
  count() %>%
  mutate(source = 'baseline_output')

# merge before plot
heating <- rbind(raw.heating, base.heating)
heating$heating <- as.factor(heating$heating)

# Now plot
ggplot(data = heating, mapping = aes(x = time, y = n, group = heating, colour = heating)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Heating', subtitle = 'Counts by Level') +
  xlab('Year') +
  ylab('Count')

heating.norm <- heating %>%
  group_by(time) %>%
  mutate(total = sum(n)) %>%
  mutate(prct = (n / total))

ggplot(data = heating.norm, mapping = aes(x = time, y = prct, fill=heating)) +
  geom_bar(stat = 'identity') +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Heating') +
  xlab('Year') +
  ylab('Proportion')

if (shall.we.save) {
  ggsave(filename = 'heating.png',
       plot = last_plot(),
       path = save.path)
}

rm(raw.heating, base.heating, heating, heating.norm)
```
